Malacology: A Programmable Storage System

### 2017-03-14 paper/0_abstract.tex
paper: fix abstract sentence, spell check, add CCS/keywords
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{abstract} Storage systems are caught between the need to evolve data
processing applications efficiently and quickly, and the increasing velocity
with which storage device technology evolves. This puts tremendous pressure on
storage systems to support rapid change both in terms of their interfaces and
their performance. But adapting storage systems can be difficult because
unprincipled changes might jeopardize years of code-hardening and performance
optimization efforts that were necessary for users to entrust their data to the
storage system. We introduce the programmable storage approach, which exposes
internal services and abstractions of the storage stack as building blocks for
higher-level services. We also build a prototype to explore how existing
abstractions of common storage system services can be leveraged to adapt to the
needs of new data processing systems and the increasing variety of storage
devices.  We illustrate the advantages and challenges of this approach by
composing existing internal abstractions into two new higher-level services: a
\newcommentone{file system} metadata load balancer and a high-performance
distributed shared-log.  The evaluation demonstrates that our services inherit
desirable qualities of the back-end storage system, including the ability to
balance load, efficiently propagate service metadata, recover from failure, and
navigate trade-offs between latency and throughput using leases.
\end{abstract}

>>>>

\begin{abstract} Storage systems need to support high-performance for
special-purpose data processing applications that run on an evolving storage
device technology landscape.  This puts tremendous pressure on storage systems
to support rapid change both in terms of their interfaces and their
performance. But adapting storage systems can be difficult because unprincipled
changes might jeopardize years of code-hardening and performance optimization
efforts that were necessary for users to entrust their data to the storage
system. We introduce the programmable storage approach, which exposes internal
services and abstractions of the storage stack as building blocks for
higher-level services. We also build a prototype to explore how existing
abstractions of common storage system services can be leveraged to adapt to the
needs of new data processing systems and the increasing variety of storage
devices.  We illustrate the advantages and challenges of this approach by
composing existing internal abstractions into two new higher-level services: a
\newcommentone{file system} metadata load balancer and a high-performance
distributed shared-log.  The evaluation demonstrates that our services inherit
desirable qualities of the back-end storage system, including the ability to
balance load, efficiently propagate service metadata, recover from failure, and
navigate trade-offs between latency and throughput using leases.
\end{abstract}

### 2017-03-14 paper/6_evaluation.tex
paper: fix abstract sentence, spell check, add CCS/keywords
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Another factor that affects performance in this environment is how much load is
on each server; these experiments quantify that effect by programming the Load
Balancing interface to control the amount of load to migrate. We call this
metric a ``migration unit".  Expressing this heuristic is not easily achievable
with outward facing tunable parameters ({\it i.e.} system knobs) but with Mantle's
programmable interface, we can force the load balancer to change its migration
units. To force the balancer into the Proxy Mode (Half) scenario in
Figure~\ref{fig:mantle-modes}, which uses migration units equal to half the
load on the current server, we can use: \texttt{ targets[whoami+1] =
mds[whoami]["load"]/2 }.

>>>>

Another factor that affects performance in this environment is how much load is
on each server; these experiments quantify that effect by programming the Load
Balancing interface to control the amount of load to migrate. We call this
metric a ``migration unit".  Expressing this heuristic is not easily achievable
with outward facing tunable parameters (i.e. system knobs) but with Mantle's
programmable interface, we can force the load balancer to change its migration
units. To force the balancer into the Proxy Mode (Half) scenario in
Figure~\ref{fig:mantle-modes}, which uses migration units equal to half the
load on the current server, we can use: \texttt{ targets[whoami+1] =
mds[whoami]["load"]/2 }.

### 2017-03-14 paper/paper.tex
paper: fix abstract sentence, spell check, add CCS/keywords
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\conferenceinfo{CONF'yy}{Month d--d, 20yy, City, ST, Country}
\copyrightyear{20yy}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}\reprintprice{\$15.00}
\copyrightdoi{nnnnnnn.nnnnnnn}

@@

% Uncomment the publication rights used.
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

@@

% 2012 ACM Computing Classification System (CSS) concepts
% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010124.10010138.10010143</concept_id>
<concept_desc>Theory of computation~Program analysis</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

@@

\keywords
keyword1, keyword2

>>>>

\CopyrightYear{2017} 
\setcopyright{acmcopyright}
\conferenceinfo{EuroSys '17,}{April 23-26, 2017, Belgrade, Serbia}
\isbn{978-1-4503-4938-3/17/04}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/3064176.3064208}

%\conferenceinfo{CONF'yy}{Month d--d, 20yy, City, ST, Country}
%\copyrightyear{20yy}
%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}\reprintprice{\$15.00}
%\copyrightdoi{nnnnnnn.nnnnnnn}

@@

% Uncomment the publication rights used.
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

@@

% 2012 ACM Computing Classification System (CSS) concepts
% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003152.10003517.10003519</concept_id>
<concept_desc>Information systems~Distributed storage</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010941.10010949.10003512</concept_id>
<concept_desc>Software and its engineering~File systems management</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992</concept_id>
<concept_desc>Software and its engineering~Software functional properties</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Distributed storage}
\ccsdesc[500]{Software and its engineering~File systems management}
\ccsdesc[300]{Software and its engineering~Software functional properties}
% end generated code

@@

\keywords
Distributed Storage, Programmability, Ceph
